Additional analysis

### 2020-01-20 analysis/02_analysis.Rmd
Update to use latest tidyverse conventions
list() instead of funs(); pivot_*() instead of gather() and spread()

```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE}
tbl_likely_tidy <- all_models_likely %>% 
  unnest(tidy) %>% 
  filter(term %in% c("theta_1", "theta_2", "theta_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

@@

```{r combine-likely-tables, results="asis"}
tbl_likely_2_header <- enframe(colnames(tbl_likely_2)) %>% 
  mutate(value = (value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_likely_1))

tbl_likely_3_header <- enframe(colnames(tbl_likely_3)) %>% 
  mutate(value = (value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_likely_1))

@@

```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE}
tbl_amounts_tidy <- all_models_amount %>% 
  unnest(tidy) %>% 
  filter(term %in% c("mu", "mu_diff", "pct_change")) %>% 
  group_by(title) %>% 
  mutate(group_id = 1:n()) %>% 
  mutate(term = case_when(
    term == "mu" ~ paste0(term, "_", group_id),
    TRUE ~ term
  )) %>% 
  select(title, term, estimate) %>% 
  spread(term, estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  ungroup()

@@

```{r combine-amount-tables, results="asis"}
tbl_amount_2_header <- enframe(colnames(tbl_amount_2)) %>% 
  mutate(value = (value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_amount_1))

tbl_amount_3_header <- enframe(colnames(tbl_amount_3)) %>% 
  mutate(value = (value)) %>% 
  spread(name, value) %>% 
  set_names(colnames(tbl_amount_1))

>>>>

```{r tbl-likely-diffs-level1, warning=FALSE, message=FALSE}
tbl_likely_tidy <- all_models_likely %>% 
  unnest(tidy) %>% 
  filter(term %in% c("theta_1", "theta_2", "theta_diff", "pct_change")) %>% 
  select(title, term, estimate) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>%
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  ))

@@

```{r combine-likely-tables, results="asis"}
tbl_likely_2_header <- enframe(colnames(tbl_likely_2)) %>% 
  mutate(value = (value)) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  set_names(colnames(tbl_likely_1))

tbl_likely_3_header <- enframe(colnames(tbl_likely_3)) %>% 
  mutate(value = (value)) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  set_names(colnames(tbl_likely_1))

@@

```{r tbl-amount-diffs-level1, warning=FALSE, message=FALSE}
tbl_amounts_tidy <- all_models_amount %>% 
  unnest(tidy) %>% 
  filter(term %in% c("mu", "mu_diff", "pct_change")) %>% 
  group_by(title) %>% 
  mutate(group_id = 1:n()) %>% 
  mutate(term = case_when(
    term == "mu" ~ paste0(term, "_", group_id),
    TRUE ~ term
  )) %>% 
  select(title, term, estimate) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  ungroup()

@@

```{r combine-amount-tables, results="asis"}
tbl_amount_2_header <- enframe(colnames(tbl_amount_2)) %>% 
  mutate(value = (value)) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  set_names(colnames(tbl_amount_1))

tbl_amount_3_header <- enframe(colnames(tbl_amount_3)) %>% 
  mutate(value = (value)) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  set_names(colnames(tbl_amount_1))

### 2020-01-20 analysis/03_additional-analysis.Rmd
Update to use latest tidyverse conventions
list() instead of funs(); pivot_*() instead of gather() and spread()

```{r build-consort}
consort <- readRDS(here("data", "derived_data", "completion_summary.rds")) %>% 
  spread(reason, n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

# Volunteering data from September 2015 only
df_volunteering <- cps_2015_data %>% 
  # Remove values not in the universe
  mutate_at(vars(VLSTATUS, VLDONATE), funs(ifelse(. == 99, NA, .)))

@@

tbl_sample_pop <- calc_sample_pop %>% 
  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
         not_hpdi_symbol = ifelse(in_hpdi, "", "^†^"),
         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
         diffs_hpdi_fancy = diffs_tidy %>%
           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
  mutate_at(vars(National, Sample, diffs_median), funs(percent)) %>% 
  select(Variable, Sample, National, 
         `∆~median~` = diffs_median,
         `95% HPDI` = diffs_hpdi_fancy)

@@

```{r avg-time, results="asis"}
time_summary <- results %>% 
  summarize_at(vars(duration), funs(Minimum = min, Maximum = max, Mean = mean, 
                                    `Standard deviation` = sd, Median = median)) %>% 
  gather(Statistic, value) %>% 
  mutate(Minutes = fmt_seconds(value)) %>% 
  select(-value)

>>>>

```{r build-consort}
consort <- readRDS(here("data", "derived_data", "completion_summary.rds")) %>% 
  pivot_wider(names_from = reason, values_from = n) %>% 
  mutate(group = 1:n(),
         assigned = Approved + `Failed first attention check`,
         issue = str_replace_all(issue, "assistance", "assist.")) %>% 
  mutate(assigned_label = glue("Allocated to Group {group}\n{crackdown}\n{issue}\n{funding} funding\n\nN = {assigned}"),
         completed_label = glue("Completed\nN = {Approved}\n\n{`Failed first attention check`} failed\nattention check"))

@@

# Volunteering data from September 2015 only
df_volunteering <- cps_2015_data %>% 
  # Remove values not in the universe
  mutate_at(vars(VLSTATUS, VLDONATE), list(~ifelse(. == 99, NA, .)))

@@

tbl_sample_pop <- calc_sample_pop %>% 
  mutate(in_hpdi = prop_test_bayes %>% map_lgl(~ .$theta_in_hpdi),
         not_hpdi_symbol = ifelse(in_hpdi, "", "^†^"),
         diffs_tidy = prop_test_bayes %>% map(~ .$tidied[2,]),
         diffs_median = diffs_tidy %>% map_dbl(~ .$estimate),
         diffs_hpdi_fancy = diffs_tidy %>%
           map2_chr(.x = diffs_tidy, .y = not_hpdi_symbol, 
                    .f = ~ format_hpdi(.x$conf.low, .x$conf.high, .y))) %>% 
  mutate_at(vars(National, Sample, diffs_median), list(percent)) %>% 
  select(Variable, Sample, National, 
         `∆~median~` = diffs_median,
         `95% HPDI` = diffs_hpdi_fancy)

@@

```{r avg-time, results="asis"}
time_summary <- results %>% 
  summarize_at(vars(duration), list(Minimum = min, Maximum = max, Mean = mean, 
                                    `Standard deviation` = sd, Median = median)) %>% 
  pivot_longer(everything(), names_to = "Statistic", values_to = "value") %>% 
  mutate(Minutes = fmt_seconds(value)) %>% 
  select(-value)
